Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
edits to section 7

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithms. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0, ;; map :log-weight to 0.0
   :result nil,       ;; map :result to nil
   ::store nil,       ;; map :store to nil
   ::mem {},          ;; map ::mem to the empty map 
   ... })
\end{lstlisting}
which records inference-relevant information under various keys
such as $\texttt{:log-weight}$ and $\texttt{::mem}$.
The full list of map entries depends on the inference
algorithm. Except for transformation of
the \texttt{mem} form (which converts a function to one with memoization), 
CPS transformation routines
are not aware of contents of \texttt{\$state}, do not access or
modify it directly, but rather just thread the state unmodified
through the computation. Algorithm-specific handlers of
checkpoints corresponding to the probabilistic forms
(\texttt{sample}, \texttt{observe}) modify the
state and reinject a new state into the computation.

>>>>

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithms. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0, ;; map :log-weight to 0.0
   :result nil,       ;; map :result to nil
   ::store nil,       ;; map ::store to nil
   ::mem {},          ;; map ::mem to the empty map 
   ... })
\end{lstlisting}
which records inference-relevant information under various keys such
as $\texttt{:log-weight}$ and $\texttt{::mem}$. The full list of map
entries depends on the inference algorithm. CPS transformation
routines are not aware of the contents of \texttt{\$state} and do not
access or modify it directly. Rather, they just thread the state
unmodified through the computation. The sole exception is the
transformation of  the \texttt{mem} form (which converts a function
to one with memoization). Algorithm-specific handlers of checkpoints
corresponding to the probabilistic forms (\texttt{sample},
\texttt{observe}) modify the state and insert an updated state into
the computation.
